% !TEX root = Master.tex

\noindent
[1] ForestEye Research GmbH und ARGUS Forstplanung, 2018: Handanweisung zur Betriebsinventur und
Forsteinrichtung in den Gräflich Bernstorff’schen Betrieben, Forstamt Gartow, Version 23.04.2018\\

\noindent
[2] Airborne laser scanning - an introduction and overview, 1999: Aloysius Wehr, Uwe Lohr, ISPRS Journal of
Photogrammetry and Remote Sensing. S. 68 - 82\\

\noindent
[3] Das Laserscanning. Eine neue Datenquelle zur Erfassung der Topographie, 2004: Karl Kraus, Paul
Dorninger, Wiener Schriften zur Geographie und Kartographie. S. 312 - 318.\\

\noindent
[4] On the distribution of a variate whose logarithm is normally distributed, 1941, Finney, D. J., Journal Royal Statiscal Society, v.7, p.155-161, 1941. Supplement.\\

\noindent
[5] Regression: Models, Methods and Applications. Berlin: Springer-Verlag. Ludwig Fahrmeir, Thomas Kneib, Stefan Lang, Brian Marx (2013) \\

\noindent
[6] Matching remotely sensed and field-measured tree size distributions. Jari Vauhkonen, Lauri Mehtätalob. Canadian Journal of Forest Research, 2015, 45(3): 353-363\\

\noindent
[7] Applied Multivariate Statistical Analysis (6th Edition), Richard A. Johnson, Dean W. Wichern. (02 April 2007)\\

\noindent
[8] factoextra: Extract and Visualize the Results of Multivariate Data Analyses, Alboukadel Kassambara and
Fabian Mundt, 2017, R package version 1.0.5 \\
https://CRAN.R-project.org/package=factoextra \\

\noindent
[9] jtools: Analysis and Presentation of Social Scientific Data, Jacob A. Long, 2018, R package version 1.1.1\\
https://cran.r-project.org/package=jtools \\

\noindent
[10] plotly: Create Interactive Web Graphics via plotly.js. R package version 4.7.1. Carson Sievert, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec and
Pedro Despouy (2017). \\
https://CRAN.R-project.org/package=plotly \\

\noindent
[11] ggplot2: Elegant Graphics for Data Analysis. H. Wickham. Springer-Verlag New York, 2016 \\

\noindent
[12] Projektbericht: Orthobild-Mosaik und Airborne Laserscanning Forsteinrichtung Gartow, Marko Pilger, GEOCART, 06.11.2018, Version 1.0\\

\noindent
[13] Mathematical Methods of Statistics. Cramer, H. (1946) Princeton University Press, Princeton.\\

\noindent
[14]  Introduction to Mathematical Statistics, 4th edition. R. V. Hogg and A. T. Craig (1978) New York: Macmillan\\

\noindent
[15]  R.A. Fisher and the making of maximum likelihood 1912-1922. Aldrich, John. (1997). Stat Sci. 12. 10.1214/ss/1030037906. \\

\noindent
[16] fitdistrplus: An R Package for Fitting Distributions. Marie Laure Delignette-Muller, Christophe Dutang (2015).  Journal of Statistical Software, 64(4), 1-34.\\
 https://cran.r-project.org/web/packages/fitdistrplus/vignettes/paper2JSS.pdf\\

\noindent
[17] MDPI and ACS Style. Estimating Individual Tree Height and Diameter at Breast Height (DBH) from Terrestrial Laser Scanning (TLS) Data at Plot Level.
Liu, G.; Wang, J.; Dong, P.; Chen, Y.; Liu, Z. Forests 2018, 9, 398.\\




